### 2021-09-11 draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@dbd6d6d0b52cba29b1d553dd908648a4fce9788d 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@e25b19d09dae84024cc8c6ee0a19767b0fe31960 🚀

\begin{itemize}
\tightlist
\item
  Click on the ``Use this template'' button
\item
  Edit this README!
\item
  Add an \texttt{ACCESS\_TOKEN} secret to your repository
\item
  Trigger a build by pushing a commit - the builds are only active on
  the \texttt{main} (\textbf{not} \texttt{master}) branch, and on pull
  requests
\item
  Go to \texttt{http://you.github.io/repo-name/} to view the html
  version and the PDFs
\item
  Add your references to the \texttt{references.bib} file
\item
  Edit the \texttt{metadata.json} file to add the title, abstract,
  authors
\item
  Edit the \texttt{manuscript.md} file to make changes to your text
\end{itemize}

>>>>

The process of deploying this template has been \emph{greatly}
streamlined from previous versions:

\begin{itemize}
\tightlist
\item
  Click on the ``Use this template'' button
\item
  Edit \texttt{README.md} with your own text, commit, and push
\item
  This push will trigger the first build - the builds are only active on
  the \texttt{main} branch (\emph{not} \texttt{master}!), and on pull
  requests
\item
  Go to \texttt{http://you.github.io/repo-name/} to view the html
  version, and get access to the PDFs
\item
  Add your references to the \texttt{references.bib} file
\item
  Edit the \texttt{metadata.json} file to add the title, abstract,
  authors
\end{itemize}

In particular, note that \emph{you do not need} to create a personnal
access token to deploy to \texttt{gh-pages} (from where the website is
served).
